Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Setting out.width="70%" as default.

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, out.width = "100%")
```

@@

```{r, echo=FALSE, out.width="70%", fig.cap="Need caption"}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

@@

```{r, echo=FALSE, out.width="70%", fig.cap="Need caption"}
knitr::include_graphics("Images/info_kreft.png")
```

@@

```{r arsresultat, echo=FALSE, out.width="70%", fig.align='center', fig.asp=0.5, fig.cap="Net income/loss data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  rename(
    Year = year,
    `Net income` = arsresultat,
    `Net positive` = annual_profit
  ) |>
  ggplot(aes(Year, `Net income`, fill = `Net positive`)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  scale_fill_green(kreftforeningen$annual_profit) +
  labs(
    x = "", y = ""
  ) +
  theme_light() +
  theme(legend.position = "none")
```

```{r egenkapital, echo=FALSE, out.width="70%", fig.align='center', fig.asp=0.5, fig.cap="Total equity/liabilities data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  ggplot(aes(year, sum_egenkapital_og_gjeld, fill = balance_positive)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  scale_fill_green(kreftforeningen$balance_positive) +
  labs(
    x = "", y = "", title = "Total equity/liabilities (in thousands)"
  ) +
  theme_light() +
  theme(legend.position = "none")
```

```{r CEO, echo=FALSE, out.width="70%", fig.align='center', fig.asp=0.618, fig.cap="CEO compensation data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  # preparing for pivoting
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |>
  # Compensation in ordinary numbers
  mutate(
    lederlonn = lederlonn * 1000,
    leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
  ) |>
  # renaming for the purposes of the plot
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |>
  # pivoting to join the two values to use fill
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  # using currency scale function to add correct currency code or ?
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  # pretty colours
  scale_fill_met_d("Hokusai2", direction = -1) +
  labs(
    x = "", y = "", title = "CEO compensation"
  ) +
  theme_light() +
  theme(legend.position = "bottom")
```

>>>>

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, out.width = "70%")
```

@@

```{r, echo=FALSE, fig.cap="Need caption"}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

@@

```{r, echo=FALSE, fig.cap="Need caption"}
knitr::include_graphics("Images/info_kreft.png")
```

@@

```{r arsresultat, echo=FALSE, fig.align='center', fig.asp=0.5, fig.cap="Net income/loss data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  rename(
    Year = year,
    `Net income` = arsresultat,
    `Net positive` = annual_profit
  ) |>
  ggplot(aes(Year, `Net income`, fill = `Net positive`)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  scale_fill_green(kreftforeningen$annual_profit) +
  labs(
    x = "", y = ""
  ) +
  theme_light() +
  theme(legend.position = "none")
```

```{r egenkapital, echo=FALSE, fig.align='center', fig.asp=0.5, fig.cap="Total equity/liabilities data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  ggplot(aes(year, sum_egenkapital_og_gjeld, fill = balance_positive)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  scale_fill_green(kreftforeningen$balance_positive) +
  labs(
    x = "", y = "", title = "Total equity/liabilities (in thousands)"
  ) +
  theme_light() +
  theme(legend.position = "none")
```

```{r CEO, echo=FALSE, fig.align='center', fig.asp=0.618, fig.cap="CEO compensation data for the Norwegian Cancer Society from Proff.no"}
kreftforeningen |>
  # preparing for pivoting
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |>
  # Compensation in ordinary numbers
  mutate(
    lederlonn = lederlonn * 1000,
    leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
  ) |>
  # renaming for the purposes of the plot
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |>
  # pivoting to join the two values to use fill
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  # using currency scale function to add correct currency code or ?
  scale_y_continuous(labels = scales::label_dollar(prefix = "NOK ")) +
  # pretty colours
  scale_fill_met_d("Hokusai2", direction = -1) +
  labs(
    x = "", y = "", title = "CEO compensation"
  ) +
  theme_light() +
  theme(legend.position = "bottom")
```
